### 2012-03-28 contents.tex
Updating QA values after removing mass verifications.

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering QA team size} & 
			\MyHead{2.5cm}{\textbf{\% of verifications by QA team}} \\
			\hline
			Eclipse/Platform        & 4 (2.4\%)  &  1.1\% \\
			Eclipse/EMF             & 0 (0.0\%)  &  0.0\% \\
			NetBeans/Platform       & 5 (21.7\%) & 93.3\% \\
			NetBeans/VersionControl & 5 (20.8\%) & 93.2\% \\
			% \bottomrule
		\end{tabular}
		\end{center}

@@

	% We counted the number of times each developer verified or fixed a bug. We consider that, if a developer is primarily concerned with quality assurance, then s/he verifies much more bugs that s/he fixes.
	% 
	% We defined ratio as ...
	% 
	% The verified/fixed ratio for the four projects is shown on Table XXX.

% \begin{verbatim}
% *** eclipse-platform 
% Verifiers: 4 (2.4%)
%   1.1% of verifications
% Fixers: 30 (17.9%)
% Total developers: 168 
% 
% *** eclipse-emf 
% Verifiers: 0 (0.0%)
%   0.0% of verifications
% Fixers: 4 (30.8%)
% Total developers: 13 
% 
% *** netbeans-platform 
% Verifiers: 5 (21.7%)
%   93.3% of verifications
% Fixers: 6 (26.1%)
% Total developers: 23 
% 
% *** netbeans-versioncontrol 
% Verifiers: 5 (20.8%)
%   93.2% of verifications
% Fixers: 6 (25.0%)
% Total developers: 24 
% \end{verbatim}

	In both NetBeans subprojects it is possible to infer the existence of a QA team, composed by approximately 20\% of the developers, that performs about 90\% of all verifications. In the Eclipse subprojects, there is no evidence of a dedicated QA team. In Eclipse/EMF no developer focus specifically on verification. In Eclipse/Platform, 2.4\% of the developers focus on verification tasks, contributing only to 1.1\% of the verifications.

>>>>

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering QA team size} & 
			\MyHead{1.5cm}{\textbf{\% of verifications by QA team}} \\
			\hline
			Eclipse & & \\
			\quad Platform        & 4 (2.4\%)  &  1.1\% \\
			\quad EMF             & 0 (0.0\%)  &  0.0\% \\
			NetBeans & & \\
			\quad Platform       & 25 (18.8\%) & 80.1\% \\
			\quad VersionControl & 5 (20.8\%) & 93.2\% \\
			% \bottomrule
		\end{tabular}
		\end{center}

@@

	In both NetBeans subprojects it is possible to infer the existence of a QA team, composed by approximately 20\% of the developers, performing at least 80\% of all verifications. In the Eclipse subprojects, there is no evidence of a dedicated QA team. In Eclipse/EMF no developer focus specifically on verification. In Eclipse/Platform, 2.4\% of the developers focus on verification tasks, contributing only to 1.1\% of the verifications.
